---
editor_options: 
  chunk_output_type: console
---
# Feuilles de route quotidiennes {#feuilleroute}

```{r feuille_route_function_FR, echo=FALSE}

feuilleroute_xlsx <- here("excel", "feuilleroute.xlsx")

graphFeuilleRoute <- function(df){
    
  df %>% 
    drop_na(desc_fr) %>% 
    select(" " = desc_fr,
         Heures = heures) %>%
    
  kbl(escape = F, # permet de passer les <br/>
      align = c("l","c")) %>%
    
    kable_styling( "striped", # "striped",      # kable_minimal ou kable_styling
                  full_width = TRUE) %>% 
    
    row_spec(which(df$param == "reunion",), bold = T, 
             color = couleurs$brunMaillot,
             background = couleurs$orangePale) %>% 
    row_spec(which(df$param == "course",), bold = T, 
             color = couleurs$bleuTour,
             background = couleurs$jauneTour, 
             font_size = 20) %>% 
    row_spec(which(df$param == "repas",), bold = F, 
             color = couleurs$blueSprintMaire,
             background = couleurs$bluePale) %>% 
    row_spec(which(df$param == "navette",), bold = T) %>% 
    row_spec(which(df$param == "arrivee",), bold = T, 
             color = couleurs$bleuTour)
    
    
}
```

## `r dates_FR %>% filter(code=="Dim_Av") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_dim_av_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "DIM_AV") %>% 
  graphFeuilleRoute()

```

<br/>

## `r dates_FR %>% filter(code=="Lun_Av") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_lun_av_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "LUN_AV") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Mar") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_mar_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "MAR") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Mer") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_mer_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "MER") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Jeu") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_jeu_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "JEU") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Ven") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_ven_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "VEN") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Sam") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_sam_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "SAM") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Dim") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_dim_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "DIM") %>% 
  graphFeuilleRoute()
```

<br/>

## `r dates_FR %>% filter(code=="Lun_Ap") %>% pull(jsem_jour_mois_an)` {-}

```{r feuille_route_lun_ap_FR, echo=FALSE}

read_excel(feuilleroute_xlsx, sheet = "LUN_AP") %>% 
  graphFeuilleRoute()
```

<br/>

