---
editor_options: 
  chunk_output_type: console
---

<!-- MedMasso_EN.Rmd  -->



# Medical assistance {#medical}


Every foreign rider must have medical insurance.  

**No insurance, no racing !**

In case of serious injury which requires hospitalization or an operation, the insurance must cover all administrative and medical charges. A team manager may have to pay the fees directly at the hospital pending the reimbursement by the insurance.



### Hospital list {-}

```{r, echo=FALSE}
resp_medical <- read_excel(staff_xlsx, sheet = "CO") %>% 
  filter(role_en == 'Medical')

```

| City          | Adress                 | Phone          |
| :------------ | :--------------------- | :------------- |
| Val-d'Or      | 725, 6e rue            | (819) 855-5858 |
| Amos          | 622, 4e rue Ouest      | (819) 732-3341 |
| Rouyn-Noranda | 4, 9e rue              | (819) 764-5131 |
| Malartic      | 1141, rue Royale       | (819) 757-4342 |
| Senneterre    | 961,rue de la Clinique | (819) 825-5858 | 
| La Sarre      | 679 2e Rue E           | (819) 333-2311 | 

<br/> 
<div style="background-color: #ffaca3; border-radius: 5px; border: 2px solid#ff3924; padding: 3px;">
  <p>Please contact the person in charge of the medical comitee **before** going to the hospital:</p> 
  <p style="justify-content: center; align-items: center;margin:10px 100px 20px 20px;">
    <table style="width:100%;text-align:center;"> 
      <tr> 
        <td width="50%"> `r resp_medical %>% pull(noms)` </td> 
        <td width="50%"> `r resp_medical %>% pull(cell)`  </td> 
      </tr> 
    </table>
  </p>
</div>


### Medical clinic schedule {-}

```{r horraire_med_EN, echo=FALSE}

med_xlsx <- here("excel", "med_masso.xlsx")

df <- read_excel(med_xlsx, sheet = "MEDICAL") 

left_join(x= df, y= dates_EN, by= "code") %>% 
  select(Date = jsem_jour_mois,
         "Opening hours" = heures) %>%   
  kbl(escape = F, # permet de passer les <br/>
      align = c("l","c")) %>% 
    kable_styling("striped",      # kable_minimal
                  full_width = TRUE) 
```


Outside these hours, cyclists should contact the reception desk to communicate with the medical team.

The medical team will be present at the starting line 1h before each race and at the finish line 30 minutes after the arrival.


### Massage clinic schedule {-}

In order to benefit from massage therapy, please register at the local in advance.

**Fees** : 20 mins session - payable in cash on site 

```{r horraire_med_EN_2, echo=FALSE}

med_xlsx <- here("excel", "med_masso.xlsx")

df <- read_excel(med_xlsx, sheet = "MASSO") 

left_join(x= df, y= dates_EN, by= "code") %>% 
  select(Date = jsem_jour_mois,
         "Opening hours" = hours) %>%   
  kbl(escape = F, # permet de passer les <br/>
      align = c("l","c")) %>% 
    kable_styling("striped",      # kable_minimal
                  full_width = TRUE) 
```

### VIP schedule {-}

All 18 years old or older coaches, mechanics, therapists, volunteers and sponsors are invited to the *salon VIP*.

From sunday `r dates_EN %>% filter(code=="Dim_Av") %>% pull(jour_mois)` to sunday `r dates_EN %>% filter(code=="Dim") %>% pull(jour_mois)`, 9PM to 3AM.

