---
output: pdf_document
latex_engine: pdflatex
header-includes:
  \usepackage{helvet}
  \renewcommand\familydefault{\sfdefault}
  
  \usepackage{graphicx}
  \usepackage{float}

  \usepackage{pifont}  

  \usepackage[english]{babel}
  \usepackage[T1]{fontenc} 
  
  \usepackage{pdfpages}
  
  \usepackage{array, multirow}
  \usepackage{tabularx, tabulary, tabu, longtable}
  \usepackage{makecell}

  \setlength{\tabcolsep}{18pt} 
  \renewcommand{\arraystretch}{2} 
  
  \usepackage{fancyhdr}
  \pagestyle{fancy}
  \fancyhead{}
  \fancyhead[C]{\bfseries\leftmark}
  \fancyfoot{}
  \fancyfoot[C]{\thepage}

  \setlength{\headheight}{13pt}
  \setlength{\parindent}{0pt}
  
  \usepackage{tikz,lipsum,lmodern}    
  \usepackage[most]{tcolorbox}
  \usepackage{tcolorbox}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r call_Libs_Vars, include=FALSE}

here::i_am("guide2024.Rproj")

# Appel des librairies et variables partagées
source(here::here("code","_LibsVars.R"))

# Dates
source(here("code", "_Dates.R"))

# Pour accès aux données du fichier excel Itineraires.xlsx
source(here("code","programmation.R"))

# Langue
lang <- "EN"

# Lien Guide web
lienWeb <- glue('{params$lienWeb}{lang}')

# Locale
## https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/locales
{if (lang == "FR") Sys.setlocale("LC_TIME", locale = "fr_CA.UTF-8") 
  else Sys.setlocale("LC_TIME", locale = "en_US.UTF-8") }

opts_chunk$set( warning = FALSE,
                message = FALSE,
                quiet=TRUE)

```
 


\begin{titlepage}

\begin{center}

\huge{\textbf{`r params$annee` Tour de l'Abitibi `r params$sponsor`}}\\

\vspace*{1.0cm}


\begin{figure}[H]
  \centering    
  \includegraphics[width=0.3\linewidth]{../img/logo/TA_Glencore.png}
\end{figure}

\vfill

\line(1,0){350}\\[2mm]

\vspace*{0.5cm}
\emph{\huge{\textbf{TECHNICAL GUIDE}}\\}
\vspace*{0.75cm}
\emph{\Large{\textbf{COURSES DETAILS}}\\}
\vspace*{0.75cm}
\Large{\textbf{`r params$edition`$^{th}$ edition}}\\
\vspace*{0.75cm}
\Large{\textbf{`r params$dates_compl_EN`}}\\
\vspace*{0.5cm}
\line(1,0){350}\\[2mm]

\vfill

Version :  `r Sys.Date()` \\

\end{center}

\end{titlepage}



\tableofcontents
\thispagestyle{empty}

\vfill

\emph{\textbf{Notes}\\}

In order to avoid wasting paper and to facilitate updates to the document, only the details of the courses will be available in paper format.

Please refer to the website : \url{`r lienWeb`} for complete technical guide information.



\newpage



\thispagestyle{plain}
\setcounter{page}{1}

\includepdf[scale=0.8,pages=1,pagecommand=\section{Schedule}]{details/prog.png}

\pagebreak

```{r include=FALSE}
Etape <- 1

jour_date <- dates_EN %>% filter(code=="Mar") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureEntree <- iti_etape$Details$HeureEntreeVille[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{Stage `r Etape` : `r iti_etape$Details$Descr_Villes[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.35\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}

\vspace*{6mm}

\begin{table}[h]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		Start & `r heureDep`\\ 
    		\*
    		Circuit entrance & `r heureEntree`\\ 
    		\*
    		Finish & `r heureArr` \\ \bottomrule

	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.6\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.8\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Neutralized start on `r iti_etape$Details$KM_Neutres[Etape]` km
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] `r iti_etape$Details$Nb_tours[Etape]` full clockwise laps of the `r iti_etape$Details$KM_par_tours[Etape]` km finish circuit
  \item[\ding{46}] The entrance to the circuit is located at the intersection of \textit{4e Rue Est} and \textit{14e Avenue Est}
  \end{itemize}
\end{tcolorbox}

\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}


\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak


```{r include=FALSE}
Etape <- 2

jour_date <- dates_EN %>% filter(code=="Mer") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{Stage `r Etape` : `r iti_etape$Details$Descr_Villes[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.2\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}



\begin{table}[H]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		Start & `r heureDep`\\ 
    		\*
    		Finish & `r heureArr` \\ \bottomrule
	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Neutralized start on `r iti_etape$Details$KM_Neutres[Etape]` km
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Finish without circuit
  \end{itemize}
\end{tcolorbox}

\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}


\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak



```{r include=FALSE}
Etape <- 3

jour_date <- dates_EN %>% filter(code=="Jeu") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

heureDernierDep <- iti_etape$Details$DerDep[Etape]

heureDernierArr <- iti_etape$Details$DerArr[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{`r iti_etape$Details$Nom_Courts_EN[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.2\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}



\begin{table}[H]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		First start & `r heureDep`\\ 
    		\*
    		First finish & `r heureArr` \\ 
        \*
    		Last start & `r heureDernierDep` \\ 
        \*
    		Last finish & `r heureDernierArr` \\ \bottomrule
	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Round-trip time trial : 2 x 5 km
  \item[\ding{46}] Team car deviation towards 3e ave Est and 1ere Rue Est
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}


\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak



```{r include=FALSE}
Etape <- 4

jour_date <- dates_EN %>% filter(code=="Jeu") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{Stage `r Etape` : `r iti_etape$Details$Descr_Villes[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.2\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}



\begin{table}[H]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		Start & `r heureDep`\\ 
    		\*
    		Finish & `r heureArr` \\ \bottomrule
	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.8\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Neutralized start on `r iti_etape$Details$KM_Neutres[Etape]` km
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.7\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Dinner will be served at the \emph{Théâtre Meglab}, near the finish line
  \end{itemize}
\end{tcolorbox}

\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}


\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak


```{r include=FALSE}
Etape <- 5

jour_date <- dates_EN %>% filter(code=="Ven") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{Stage `r Etape` : `r iti_etape$Details$Descr_Villes[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.2\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}



\begin{table}[H]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		Start & `r heureDep`\\ 
    		\*
    		Finish & `r heureArr` \\ \bottomrule
	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.6\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.85\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Neutralized start on `r iti_etape$Details$KM_Neutres[Etape]` km
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Finish without circuit
  \end{itemize}
\end{tcolorbox}

\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}


\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak


```{r include=FALSE}
Etape <- 6

jour_date <- dates_EN %>% filter(code=="Sam") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{Stage `r Etape` : `r iti_etape$Details$Descr_Villes[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.2\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}



\begin{table}[H]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		Start & `r heureDep`\\ 
    		\*
    		Finish & `r heureArr` \\ \bottomrule
	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.6\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.8\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Neutralized start on `r iti_etape$Details$KM_Neutres[Etape]` km
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Finish without circuit
  \end{itemize}
\end{tcolorbox}

\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}


\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak





```{r include=FALSE}
Etape <- 7

jour_date <- dates_EN %>% filter(code=="Dim") %>% pull(jsem_jour_mois_an)

heureDep <- iti_etape$Details$time_depart[Etape]

heureEntree <- iti_etape$Details$HeureEntreeVille[Etape]

heureArr <- iti_etape$Details$time_arrivee[Etape]

comm <- here("img", "logo",  glue("comm_{Etape}.png"))
```

\thispagestyle{plain}
\section{Stage `r Etape` : `r iti_etape$Details$Descr_Villes[Etape]`}


\begin{table}[H]
\centering
\begin{tabularx}{\textwidth}{X X}
	  \large{\textbf{`r jour_date`}}  & \multicolumn{1}{r}{\multirow{2}{*}{\includegraphics[width=0.35\textwidth]{`r comm`}}} \\
	  \textbf{`r iti_etape$Details$KM_Total[Etape]` km}  &  \textbf{} \\
  \end{tabularx}
\end{table}

\vspace*{8mm}

\begin{table}[h]
\centering
		\begin{tabular}{m{6cm} c}
    		\textbf{} & \textbf{Time} \\ \toprule
    		Start & `r heureDep`\\ 
    		\*
    		Circuit entrance & `r heureEntree`\\ 
    		\*
    		Finish & `r heureArr` \\ \bottomrule

	\end{tabular}
\end{table}



\subsection{Course}

\begin{figure}[H]
  \centering    
  \includegraphics[width=1\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Full.png"))`}
\end{figure}

\pagebreak

\subsection{Start details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=0.9\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Dep.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] Neutralized start on `r iti_etape$Details$KM_Neutres[Etape]` km
  \end{itemize}
\end{tcolorbox}


\subsection{Finish details}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "cartes", params$input_output,  glue("Etape{Etape}_Arr.png"))`}
\end{figure}

\begin{tcolorbox}[colback=orange!5!white,colframe=orange!75!black]
  \begin{itemize}
  \item[\ding{46}] `r iti_etape$Details$Nb_tours[Etape]` full clockwise laps of the `r iti_etape$Details$KM_par_tours[Etape]` km finish circuit
  \item[\ding{46}] The entrance to the circuit is located at the intersection of \textit{4e Rue Est} and \textit{14e Avenue Est}
  \end{itemize}
\end{tcolorbox}

\pagebreak

\subsection{Elevation}

\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Full_{lang}.png"))`}
\end{figure}


\begin{figure}[H]
  \centering    
  \includegraphics[width=\textwidth]{`r here("img", "elev", glue("Etape{Etape}_Final_{lang}.png"))`}
\end{figure}

\pagebreak

\includepdf[scale=.9]{`r here("guide_EN_PDF", "details", glue("tableau_{Etape}.pdf"))`}

\pagebreak

